Writing a reproducible paper with RStudio and Quarto

### 2023-04-18 paper.qmd
fixed YAML header with HTML output, changed two reference to this in the text

---
title: "Writing a reproducible paper with RStudio and Quarto"
author:
  - name: Paul C. Bauer
    orcid: 0000-0002-8382-9724
    email: mail@paulcbauer.de
    affiliations:
      - name: Mannheim Centre for European Social Research
  - name: Camille Landesvatter
    orcid: 0000-0003-0156-5364
    email: camille.landesvatter@uni-mannheim.de
    affiliations:
      - name: Mannheim Centre for European Social Research
format:
  pdf:
    number-sections: true
    colorlinks: true
    keeptex: true
    include-in-header: 
      text: |
        \usepackage{booktabs}
        \usepackage{siunitx}
        \newcolumntype{d}{S[
            input-open-uncertainty=,
            input-close-uncertainty=,
            parse-numbers = false,
            table-align-text-pre=false,
            table-align-text-post=false
         ]}
date: 'last-modified'
date-format: '[This version:] MMMM D, YYYY [<br>(First version: February  16, 2023)]'
abstract: 'This paper provides a template to write a reproducible scientific paper with RStudio and Quarto. It falls into a series of other templates, namely using RMarkdown [@Bauer2018-dl] (see [here](https://osf.io/k8jhx/)) and Pagedown [@Bauer2021-dl] (see [here](https://osf.io/q395s)). Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/) (click on ![](githubcode.png) $\Rightarrow$ **Download ZIP**). We are convinced that in the future there will be many improvements and developments with regards to RStudio and Quarto. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/). To compile this PDF document please first read @sec-prerequisites.'
bibliography: references.bib
csl: american-sociological-association.csl
tbl-cap-location: top
number-sections: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
editor:
  mode: source
---

@@

If you want your document to be rendered in multiple output formats (e.g., HTML and PDF, like we did here), you need to specify both outputs in your YAML header. **Take `paper.qmd` (the underlying quarto file of this pdf) and have a look at the YAML (line #14 - #16) to see how to specify different outputs.** (There is just pdf output specified no html)

@@

-   first, use the Render Button in R Studio. If you click it without using the drop down menu, by default it will create HTML since it is the first format listed in our YAML. Always remember to specify your desired output formats in your YAML (as described in @sec-basics-2) **If you use the drop down menu of the "Render"-button, you can specify the desired output (e.g., HTML or PDF) but only if you specified it in your YAML.** (again: not possible here because just one output defined)

>>>>

---
title: "Writing a reproducible paper with RStudio and Quarto"
author:
  - name: Paul C. Bauer
    orcid: 0000-0002-8382-9724
    email: mail@paulcbauer.de
    affiliations:
      - name: Mannheim Centre for European Social Research
  - name: Camille Landesvatter
    orcid: 0000-0003-0156-5364
    email: camille.landesvatter@uni-mannheim.de
    affiliations:
      - name: Mannheim Centre for European Social Research
format:
  html:
    toc: true
    toc_float: true
    toc_depth: 2
    number_sections: true
    code_folding: hide
    theme: readable
  pdf:
    number-sections: true
    colorlinks: true
    keeptex: true
    include-in-header: 
      text: |
        \usepackage{booktabs}
        \usepackage{siunitx}
        \newcolumntype{d}{S[
            input-open-uncertainty=,
            input-close-uncertainty=,
            parse-numbers = false,
            table-align-text-pre=false,
            table-align-text-post=false
         ]}
date: 'last-modified'
date-format: '[This version:] MMMM D, YYYY [<br>(First version: February  16, 2023)]'
abstract: 'This paper provides a template to write a reproducible scientific paper with RStudio and Quarto. It falls into a series of other templates, namely using RMarkdown [@Bauer2018-dl] (see [here](https://osf.io/k8jhx/)) and Pagedown [@Bauer2021-dl] (see [here](https://osf.io/q395s)). Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/) (click on ![](githubcode.png) $\Rightarrow$ **Download ZIP**). We are convinced that in the future there will be many improvements and developments with regards to RStudio and Quarto. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/). To compile this PDF document please first read @sec-prerequisites.'
bibliography: references.bib
csl: american-sociological-association.csl
tbl-cap-location: top
number-sections: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
editor:
  mode: source
---

@@

If you want your document to be rendered in multiple output formats (e.g., HTML and PDF, like we did here), you need to specify both outputs in your YAML header. Take `paper.qmd` (the underlying quarto file of this pdf) and have a look at the YAML (line #15 - #22) to see how to specify different outputs.

@@

-   first, use the Render Button in R Studio. If you click it without using the drop down menu, by default it will create HTML since it is the first format listed in our YAML. Always remember to specify your desired output formats in your YAML (as described in @sec-basics-2) If you use the drop down menu of the "Render"-button, you can specify the desired output (e.g., HTML or PDF) but only if you specified it in your YAML.
